---
title: "Project 2 - Regression"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Project 2 - Regression}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(MATH4753ROSAproj2)
```

# Introduction

This package contains functions to perform regression analysis; in this case, both SLR and Piecewise Regression. Below are examples of the functions. There is also a shiny app which may be called with a function as well.

# The Function `myciplot`

This function performs a SLR analysis on the `lm()` of data set and produces a histogram, a residual diagnostic plot, and a named list with everything you could ever wish for to tickle an regression fancy one might have.

```{r, fig.align = "center", fig.width=7, fig.height=5}
ylm <- lm(PIPE ~ GUESS, data = dow)

myciplot(x = ylm, alpha = 0.05, f = 0.6)
```

# The Function `myknot`

This function helps us in finding the $x_k$ which will maximize $R^2$. It produces an $R^2$ value. We use this function again to find a better estimate than what human eyes can estimate.

```{r}
myknot(x_k = 17, x = spruce.df$BHDiameter, y = spruce.df$Height, data = spruce.df)
```

Based on this $x_k$, almost $77 \%$ of the variation can be explained by the explanatory variable `BHDiameter`. I think we can do better!

```{r}
diam <- spruce.df$BHDiameter
  height <- spruce.df$Height
  
  x <- seq(min(diam), max(diam), length = 1000)
  y <- vector(mode = "numeric", length = 1000)
  
  for(i in 1:1000){
    y[i] <- myknot(x[i], x = spruce.df$BHDiameter, y = spruce.df$Height, data=spruce.df)
  }
  
  nmax <- which.max(y)
  
  plot(x, y, type = "l",lwd = 2, col = "blue", ylab = "Rsquared", xlab = "xk", main = "Rsquared ~ xk")
  abline(v = x[nmax], lwd = 3, col = "maroon")
  text(x = x[nmax] - 0.5, 
       y = 0.68, 
       srt=90, 
       paste0(round(x[nmax], 4)))
  x[nmax]
```

Here we have a wonky plot, but it displays where the maximum $R^2$ is and returns the corresponding $x_k$. I think we can do better!

```{r}
optimize(myknot,
         interval = c(15,20),
         x = spruce.df$BHDiameter,
         y = spruce.df$Height,
         maximum = TRUE)
```

Using the `optimize()` function produced slightly different results. It turns out this these values are more accurate for the model! 

> NOTE: The above statment can be justfied using the `segmented()` function from the `segmented` package in `R` (calculation omitted).














